Risk Perceptions for Wearable Devices

### 2015-03-06 tex-inputs/conclusion.tex
pass through conclusion

Our survey of 1,784 Internet users for their perceptions of wearable devices was the first large-scale study to investigate user security and privacy concerns for wearable devices. We identify that participants are most concerned about protecting their financial information, photos, or videos and least concerned about demographic or biometric data. We find that participants have a significant difference in perception of risk when data is being shared with an application's server versus other human recipients, and also that certain data is more comfortably shared with certain recipients. Participants' self-reported concerns of new wearable device capabilities are also presented to give a sense of the relevant user concerns, which can be used to guide future research in privacy with respect to wearable devices, especially warnings, notifications, and permissions. We perform two regression model analyses with respect to the type of data and the associated risks to verify our results.

>>>>

Our survey of 1,784 Internet users for their perceptions of wearable devices was the first large-scale study to investigate user security and privacy concerns for wearable devices. We identify that participants are most concerned about protecting their financial information, photos, or videos and least concerned about demographic or biometric data. We find that participants have a significant difference in perception of risk when data is being shared with an application's server versus other human recipients. Participants' self-reported concerns of new wearable device capabilities are also presented to give a sense of the relevant user concerns, which can be used to guide future research in privacy with respect to wearable devices, especially warnings, notifications, and permissions. We perform two regression model analyses with respect to the type of data and the associated risks to verify our results.
